Supporting Information:\\ NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PE and PG lipids

### 2021-04-05 manuscriptPGPEsuppl.tex
Update manuscriptPGPEsuppl.tex

\author{Jesper J. Madsen}
\affiliation[University of Chicago]{Department of Chemistry, The University of Chicago, Chicago, Illinois, United States of America}
\alsoaffiliation[University of South Florida]{Department of Global Health, College of Public Health, University of South Florida, Tampa, Florida, United States of America}

@@

\noindent
{\it Jesper J. Madsen}
%% Please write description of your contribution here

>>>>

\author{Jesper J. Madsen}
\affiliation[University of Chicago]{Department of Chemistry, The University of Chicago, Chicago, Illinois, United States of America}
\alsoaffiliation[University of South Florida]{Global and Planetary Health, College of Public Health, University of South Florida, Tampa, Florida, United States of America}

@@

\noindent
{\it Jesper J. Madsen}
set up, performed, and analysed several of the CHARMM36 simulations.
Provided comments on the manuscript.
